New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-09 Manuscript/Manuscript.Rmd
Continue with Results

---
title: New insights into the Weddell Sea ecosystem applying a network approach
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Tomás I.
    surname: Marina
    affiliation: "1, *"
    email: tomasimarina@gmail.com
  - given_name: Leonardo A.
    surname: Saravia
    affiliation: "1, *"
    email: arysar@gmail.com
  - given_name: Susanne
    surname: Kortsch
    affiliation: 2
    # authors can have multiple affiliations, which can also be used to mark deceased coauthors
# If you have more than one corresponding author, add them manually using the following structure (note the commas):
# Two authors: Daniel Nüst (daniel.nuest@uni-muenster.de) and Josiah Carberry (j.carberry@orcid.org)
# Three authors or more: Daniel Nüst (daniel.nuest@uni-muenster.de), Josiah Carberry (j.carberry@orcid.org), and Markus Konkol (m.konkol@wwu.de)
# If the following line is uncommented, the "corresponding: true" above are ignored
correspongdingauthors: Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A. Saravia (arysar@gmail.com)
# If authors contributed equally, please mark the respective author names with an asterisk '*' and add a further affiliation: 'These authors contributed equally to this work.'", see template.
affiliation:
  - code: 1
    address: Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina
  - code: 2
    address: University of Helsinki, Helsinki, Finland
  - code: "*"
    address: These authors contributed equally to this work.
abstract: |
  The abstract goes here.
  It can also be on _multiple lines_.
bibliography: ../WeddellSea.bib
running:
  title: New insights into the Weddell Sea food web
  author: Marina et al.
competinginterests: |
  The authors declare no competing interests.
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
# copyrightstatement: |
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #  use this to add a statement when having only software code available
  #  use this to add a statement when having only data sets available
  #code: |
  #data: |
codedata: |
    R code and data set used in this work is available at https://github.com/EcoComplex/WeddellSea
#   sample: |
# videosupplement: |
authorcontribution: |
  TIM and LAS: Conceptualization (lead); Data curation (lead); Formal analysis (lead); Methodology (lead); Coding (lead); Writing – original draft (lead); Writing – review and editing (lead). SK: Conceptualization (lead); Formal analysis (supporting); Methodology (supporting); Coding (supporting); Writing – original draft (supporting); Writing – review and editing (supporting).
# disclaimer: |
  # We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
appendix: |
  \section{Figures and tables in appendices}
  \subsection{Option 1}
  If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
  They will be correctly named automatically.
  \subsection{Option 2}
  If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.

  `\appendixfigures` needs to be added in front of appendix figures
  `\appendixtables` needs to be added in front of appendix tables

  Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
  Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
  To rename them correctly to A1, A2, etc., please add the following commands in front of them:
output:
  rticles::copernicus_article: 
    highlight: NULL
    keep_tex: true
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
editor_options: 
  markdown: 
    wrap: 72
---

@@

The main equation we used for estimating the interaction strength IS is:
```{=tex}
\begin{equation}
IS = \alpha x_R \frac{m_R}{m_C}
\end{equation}
```

@@

As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions. After exploring the distribution of the interaction strength among the species of the food web, we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].

As unweighted properties we used: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.

Formulas used to obtain the mentioned species properties are described in Appendix A1.

@@

Finally, we run extinction simulations and estimated its impact on the stability of the network. For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008]. With the aim of analysing the effect of each species on the food web's stability, we deleted one species at a time, so the network size was reduced by one. After each species extinction, we calculated the QSS for the food web minus one species (size = 489) and compared it with the QSS for the whole network (size = 490); we performed 1000 simulations for each species. Then we statistically analysed such difference with an Anderson-Darling test [@Scholz1987].
The formula for the QSS is described in Appendix A2.

@@

In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions (Figure 3).

@@

The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 4, Table 1). Regarding the distribution of the mean interaction strength among the species of the food web, the clustering method shows that species can be classified in two groups: 'High' and 'Low' interaction strength.

@@

@@

Clustering in 2 groups: high and low IS
Linear regressions btw IS (weighted) and unweighted prop.
Biplots btw QSS difference and weighted and unweighted prop.

# Examples from the official template

## FIGURES

When figures and tables are placed at the end of the MS (article in
one-column style), please add \clearpage between bibliography and first
table and/or figure as well as between each table and/or figure.

### ONE-COLUMN FIGURES

```{r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("Nikolaus_Kopernikus.jpg")
```

### TWO-COLUMN FIGURES

```{r, out.width = "12cm", echo = FALSE, fig.cap = "two column figure"}
knitr::include_graphics("Nikolaus_Kopernikus.jpg")
```

## TABLES

You can add \LaTeX table in an R Markdown document to meet the template
requirements.

### ONE-COLUMN TABLE

```{=tex}
\begin{table}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table Footnotes}
\end{table}
```
### TWO-COLUMN TABLE

```{=tex}
\begin{table*}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table footnotes}
\end{table*}
```
## MATHEMATICAL EXPRESSIONS

All papers typeset by Copernicus Publications follow the math
typesetting regulations given by the IUPAC Green Book (IUPAC:
Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell
Science, available at:
<http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf>,
1993).

Physical quantities/variables are typeset in italic font (t for time, T
for Temperature)

Indices which are not defined are typeset in italic font (x, y, z, a, b,
c)

Items/objects which are defined are typeset in roman font (Car A, Car B)

Descriptions/specifications which are defined by itself are typeset in
roman font (abs, rel, ref, tot, net, ice)

Abbreviations from 2 letters are typeset in roman font (RH, LAI)

Vectors are identified in bold italic font using \vec{x}

Matrices are identified in bold roman font

Multiplication signs are typeset using the LaTeX commands `\times` (for
vector products, grids, and exponential notations) or `\cdot`

The character \* should not be applied as mutliplication sign

## EQUATIONS

### Single-row equation

Unnumbered equations (i.e. using `$$` and getting inline preview in
RStudio) are not supported by Copernicus.

```{=tex}
\begin{equation}
1 \times 1 \cdot 1 = 42
\end{equation}
```
```{=tex}
\begin{equation}
A = \pi r^2
\end{equation}
```
```{=tex}
\begin{equation}
x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  
\end{equation}
```
### Multiline equation

```{=tex}
\begin{align}
& 3 + 5 = 8\\
& 3 + 5 = 8\\
& 3 + 5 = 8
\end{align}
```
## MATRICES

$$
\begin{matrix}
x & y & z\\
x & y & z\\
x & y & z\\
\end{matrix}
$$

## ALGORITHM/PROGRAMMING CODE

If you want to use algorithms, you need to make sure yourself that the
\LaTeX packages `algorithms` and `algorithmicx` are installed so that
`algorithm.sty` respectively `algorithmic.sty` can be loaded by the
Copernicus template. Both need to be available through your preferred
\LaTeX{} distribution. With TinyTeX (or TeX Live), you can do so by
running `tinytex::tlmgr_install(c("algorithms", "algorithmicx"))`

```{r, echo = FALSE, eval = tinytex::is_tinytex()}
tinytex::tlmgr_install(c("algorithms", "algorithmicx"))
```

Copernicus staff will no accept any additional packages from your LaTeX
source code, so please stick to these two acceptable packages. They are
needed to use the example below

```{=tex}
\begin{algorithm}
\caption{Algorithm Caption}
\label{a1}
\begin{algorithmic}
\STATE $i\gets 10$
\IF {$i\geq 5$} 
        \STATE $i\gets i-1$
\ELSE
        \IF {$i\leq 3$}
                \STATE $i\gets i+2$
        \ENDIF
\ENDIF
\end{algorithmic}
\end{algorithm}
```
## CHEMICAL FORMULAS AND REACTIONS

For formulas embedded in the text, please use `\chem{}`, e.g.
\chem{A \rightarrow B}.

The reaction environment creates labels including the letter R, i.e.
(R1), (R2), etc.

-   `\rightarrow` should be used for normal (one-way) chemical reactions

-   `\rightleftharpoons` should be used for equilibria

-   `\leftrightarrow` should be used for resonance structures

```{=tex}
\begin{reaction}
A \rightarrow B \\
\end{reaction}
\begin{reaction}
Coper \rightleftharpoons nicus \\
\end{reaction}
\begin{reaction}
Publi \leftrightarrow cations
\end{reaction}
```
## PHYSICAL UNITS

Please use `\unit{}` (allows to save the math/`$` environment) and apply
the exponential notation, for example $3.14\,\unit{km\,h^{-1}}$ (using
LaTeX mode: `\( 3.14\,\unit{...} \)`) or \unit{0.872\,m\,s^{-1}} (using
only `\unit{0.872\,m\,s^{-1}}`).

\conclusions[Conclusions]

>>>>

---
title: New insights into the Weddell Sea ecosystem applying a network approach
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Tomás I.
    surname: Marina
    affiliation: "1, *"
    email: tomasimarina@gmail.com
  - given_name: Leonardo A.
    surname: Saravia
    affiliation: "1, *"
    email: arysar@gmail.com
  - given_name: Susanne
    surname: Kortsch
    affiliation: 2
    # authors can have multiple affiliations, which can also be used to mark deceased coauthors
# If you have more than one corresponding author, add them manually using the following structure (note the commas):
# Two authors: Daniel Nüst (daniel.nuest@uni-muenster.de) and Josiah Carberry (j.carberry@orcid.org)
# Three authors or more: Daniel Nüst (daniel.nuest@uni-muenster.de), Josiah Carberry (j.carberry@orcid.org), and Markus Konkol (m.konkol@wwu.de)
# If the following line is uncommented, the "corresponding: true" above are ignored
correspongdingauthors: Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A. Saravia (arysar@gmail.com)
# If authors contributed equally, please mark the respective author names with an asterisk '*' and add a further affiliation: 'These authors contributed equally to this work.'", see template.
affiliation:
  - code: 1
    address: Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina
  - code: 2
    address: University of Helsinki, Helsinki, Finland
  - code: "*"
    address: These authors contributed equally to this work.
abstract: |
  The abstract goes here.
  It can also be on _multiple lines_.
bibliography: ../WeddellSea.bib
running:
  title: New insights into the Weddell Sea food web
  author: Marina et al.
competinginterests: |
  The authors declare no competing interests.
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
# copyrightstatement: |
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #  use this to add a statement when having only software code available
  #  use this to add a statement when having only data sets available
  #code: |
  #data: |
codedata: |
    R code and data set used in this work is available at https://github.com/EcoComplex/WeddellSea
#   sample: |
# videosupplement: |
authorcontribution: |
  TIM and LAS: Conceptualization (lead); Data curation (lead); Formal analysis (lead); Methodology (lead); Coding (lead); Writing – original draft (lead); Writing – review and editing (lead). SK: Conceptualization (lead); Formal analysis (supporting); Methodology (supporting); Coding (supporting); Writing – original draft (supporting); Writing – review and editing (supporting).
# disclaimer: |
  # We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
# appendix: |
#   \section{Figures and tables in appendices}
#   \subsection{Option 1}
#   If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
#   They will be correctly named automatically.
#   \subsection{Option 2}
#   If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
#   
#   `\appendixfigures` needs to be added in front of appendix figures
#   `\appendixtables` needs to be added in front of appendix tables
#   
#   Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
#   Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
#   To rename them correctly to A1, A2, etc., please add the following commands in front of them:
output:
  rticles::copernicus_article: 
    highlight: NULL
    keep_tex: true
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
editor_options: 
  markdown: 
    wrap: 72
---

@@

The main equation we used for estimating the interaction strength IS is:

```{=tex}
\begin{equation}
IS = \alpha x_R \frac{m_R}{m_C}
\end{equation}
```

@@

As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions. After exploring the distribution of the species log(mean interaction strength), we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979]. Then we tested the goodness of this clustering measure with the Gap statistic, which compares log(W(k)) with E*[log(W(k))] where the latter is defined via bootstraping [@Tibshirani2001].

On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.

With the aim of studying the relationship between the interaction strength of the species and its unweighted properties, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties. The statistical significance of the fitted slopes was tested, as well as the difference between the groups' slopes applying least-squares means [@Harvey1960].

Formulas used to obtain the above species properties are described in Supplementary Material.

@@

Finally, we run extinction simulations and estimated its impact on the stability of the network. For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008]. With the aim of analysing the effect of each species on the food web's stability, we deleted one species at a time, so the network size was reduced by one. After each species extinction, we calculated the QSS for the food web minus one species (size = 489) and compared it with the QSS for the whole network (size = 490); we performed 1000 simulations for each species. Then we statistically analysed such difference with an Anderson-Darling test [@Scholz1987].
The formula for the QSS is described in Supplementary Material.

@@

In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions (Figure 3). The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 4, Table 1).

Regarding the distribution of the species mean interaction strength, the clustering method showed that species do form two distinct groups: 'High' and 'Low' interaction strength (Appendix Fig. A1). The so-called 'High IS' and 'Low IS' groups of species, exhibited different and for some cases opposite relationships with unweighted properties. It's noteworthy that only the relationship with trophic level revealed a similar trend in the regression analysis for both groups: mean interaction strength increases with trophic level (Figure 5A). On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships between groups. This means that in species with relatively higher interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B). Regarding trophic similarity, the interaction strength decreases in 'High IS' species while increases in 'Low IS' species (Figure 5C).

Linear regressions btw IS (weighted) and unweighted prop.
Biplots btw QSS difference and weighted and unweighted prop.

\clearpage
\conclusions[Conclusions]

@@

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (interaction strength) and unweighted species properties. Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C). All regression slopes are statistically significant as well as group's slopes (p < 0.05)."}
knitr::include_graphics("Regressions.jpg")
```

@@

\appendixfigures
\clearpage

```{r, out.width = "12cm", echo = FALSE, fig.cap = "A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web. B) Visualization of the optimal number of clusters applying the Gap statistic."}
knitr::include_graphics("Clus_meanIS.jpg")
```

### 2022-08-09 Manuscript/Manuscript.tex
Continue with Results

As weighted property we took into account the mean interaction strength,
meaning the average strength of all interactions. After exploring the
distribution of the interaction strength among the species of the food
web, we decided to apply the k-means clustering method, which aims to
partition the species into k groups such that the sum of squares from
points to the assigned cluster centres is minimized
\citep{Hartigan1979}.

As unweighted properties we used: a) degree or the total number of
trophic interactions, taking into account in- and out-interactions (role
as predator and prey, respectively); b) trophic level or the position in
the food web relative to primary producers/detritus; and c) trophic
similarity or the trophic overlap between species based on shared and
unique resources and consumers.

Formulas used to obtain the mentioned species properties are described
in Appendix A1.

@@

Finally, we run extinction simulations and estimated its impact on the
stability of the network. For this, we calculated a stability index
called Quasi-Sign Stability (QSS), which is the proportion of stable
networks using randomized Jacobians and keeping the predator-prey sign
structure fixed \citep{Allesina2008}. With the aim of analysing the
effect of each species on the food web's stability, we deleted one
species at a time, so the network size was reduced by one. After each
species extinction, we calculated the QSS for the food web minus one
species (size = 489) and compared it with the QSS for the whole network
(size = 490); we performed 1000 simulations for each species. Then we
statistically analysed such difference with an Anderson-Darling test
\citep{Scholz1987}. The formula for the QSS is described in Appendix A2.

@@

In this work we have estimated the interaction strength for the most
highly-resolved marine food web to date, which comprises 490 species and
16041 predator-prey interactions (Figure 3).

@@

The distribution of the interaction strength best fit to a log-Normal
model, which indicates that there is a prevalent skew towards weaker
interactions (Figure 4, Table 1). Regarding the distribution of the mean
interaction strength among the species of the food web, the clustering
method shows that species can be classified in two groups: `High' and
`Low' interaction strength.

@@

\begin{table}[t]
\caption{Model comparison (AIC) for the distribution of interaction strengths of the Weddell Sea food web.}
\begin{tabular}{l c c c}
\tophline

@@

Clustering in 2 groups: high and low IS Linear regressions btw IS
(weighted) and unweighted prop. Biplots btw QSS difference and weighted
and unweighted prop.

\section{Examples from the official template}

\subsection{FIGURES}

When figures and tables are placed at the end of the MS (article in
one-column style), please add \clearpage between bibliography and first
table and/or figure as well as between each table and/or figure.

\subsubsection{ONE-COLUMN FIGURES}

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
\end{figure}

\subsubsection{TWO-COLUMN FIGURES}

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
\end{figure}

\subsection{TABLES}

You can add \LaTeX table in an R Markdown document to meet the template
requirements.

\subsubsection{ONE-COLUMN TABLE}

\begin{table}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table Footnotes}
\end{table}

\subsubsection{TWO-COLUMN TABLE}

\begin{table*}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table footnotes}
\end{table*}

\subsection{MATHEMATICAL EXPRESSIONS}

All papers typeset by Copernicus Publications follow the math
typesetting regulations given by the IUPAC Green Book (IUPAC:
Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell
Science, available at:
\url{http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf},
1993).

Physical quantities/variables are typeset in italic font (t for time, T
for Temperature)

Indices which are not defined are typeset in italic font (x, y, z, a, b,
c)

Items/objects which are defined are typeset in roman font (Car A, Car B)

Descriptions/specifications which are defined by itself are typeset in
roman font (abs, rel, ref, tot, net, ice)

Abbreviations from 2 letters are typeset in roman font (RH, LAI)

Vectors are identified in bold italic font using \vec{x}

Matrices are identified in bold roman font

Multiplication signs are typeset using the LaTeX commands
\texttt{\textbackslash{}times} (for vector products, grids, and
exponential notations) or \texttt{\textbackslash{}cdot}

The character * should not be applied as mutliplication sign

\subsection{EQUATIONS}

\subsubsection{Single-row equation}

Unnumbered equations (i.e.~using \texttt{\$\$} and getting inline
preview in RStudio) are not supported by Copernicus.

\begin{equation}
1 \times 1 \cdot 1 = 42
\end{equation}

\begin{equation}
A = \pi r^2
\end{equation}

\begin{equation}
x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  
\end{equation}

\subsubsection{Multiline equation}

\begin{align}
& 3 + 5 = 8\\
& 3 + 5 = 8\\
& 3 + 5 = 8
\end{align}

\subsection{MATRICES}

\[
\begin{matrix}
x & y & z\\
x & y & z\\
x & y & z\\
\end{matrix}
\]

\subsection{ALGORITHM/PROGRAMMING CODE}

If you want to use algorithms, you need to make sure yourself that the
\LaTeX packages \texttt{algorithms} and \texttt{algorithmicx} are
installed so that \texttt{algorithm.sty} respectively
\texttt{algorithmic.sty} can be loaded by the Copernicus template. Both
need to be available through your preferred \LaTeX{} distribution. With
TinyTeX (or TeX Live), you can do so by running
\texttt{tinytex::tlmgr\_install(c("algorithms",\ "algorithmicx"))}

\begin{verbatim}
## tlmgr update --all --self
\end{verbatim}

\begin{verbatim}
## tlmgr install algorithms algorithmicx
\end{verbatim}

Copernicus staff will no accept any additional packages from your LaTeX
source code, so please stick to these two acceptable packages. They are
needed to use the example below

\begin{algorithm}
\caption{Algorithm Caption}
\label{a1}
\begin{algorithmic}
\STATE $i\gets 10$
\IF {$i\geq 5$} 
        \STATE $i\gets i-1$
\ELSE
        \IF {$i\leq 3$}
                \STATE $i\gets i+2$
        \ENDIF
\ENDIF
\end{algorithmic}
\end{algorithm}

\subsection{CHEMICAL FORMULAS AND REACTIONS}

For formulas embedded in the text, please use
\texttt{\textbackslash{}chem\{\}}, e.g. \chem{A \rightarrow B}.

The reaction environment creates labels including the letter R, i.e.
(R1), (R2), etc.

\begin{itemize}
\item
  \texttt{\textbackslash{}rightarrow} should be used for normal
  (one-way) chemical reactions
\item
  \texttt{\textbackslash{}rightleftharpoons} should be used for
  equilibria
\item
  \texttt{\textbackslash{}leftrightarrow} should be used for resonance
  structures
\end{itemize}

\begin{reaction}
A \rightarrow B \\
\end{reaction}
\begin{reaction}
Coper \rightleftharpoons nicus \\
\end{reaction}
\begin{reaction}
Publi \leftrightarrow cations
\end{reaction}

\subsection{PHYSICAL UNITS}

Please use \texttt{\textbackslash{}unit\{\}} (allows to save the
math/\texttt{\$} environment) and apply the exponential notation, for
example \(3.14\,\unit{km\,h^{-1}}\) (using LaTeX mode:
\texttt{\textbackslash{}(\ 3.14\textbackslash{},\textbackslash{}unit\{...\}\ \textbackslash{})})
or \unit{0.872\,m\,s^{-1}} (using only
\texttt{\textbackslash{}unit\{0.872\textbackslash{},m\textbackslash{},s\^{}\{-1\}\}}).

\conclusions[Conclusions]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Figures and tables in appendices}
\subsection{Option 1}

If you sorted all figures and tables into the sections of the text,
please also sort the appendix figures and appendix tables into the
respective appendix sections. They will be correctly named
automatically.

\subsection{Option 2}

If you put all figures after the reference list, please insert appendix
tables and figures after the normal tables and figures.

\texttt{\textbackslash{}appendixfigures} needs to be added in front of
appendix figures \texttt{\textbackslash{}appendixtables} needs to be
added in front of appendix tables

Please add \texttt{\textbackslash{}clearpage} between each table and/or
figure. Further guidelines on figures and tables can be found below.
Regarding figures and tables in appendices, the following two options
are possible depending on your general handling of figures and tables in
the manuscript environment: To rename them correctly to A1, A2, etc.,
please add the following commands in front of them:
\noappendix

>>>>

As weighted property we took into account the mean interaction strength,
meaning the average strength of all interactions. After exploring the
distribution of the species log(mean interaction strength), we decided
to apply the k-means clustering method, which aims to partition the
species into k groups such that the sum of squares from points to the
assigned cluster centres is minimized \citep{Hartigan1979}. Then we
tested the goodness of this clustering measure with the Gap statistic,
which compares log(W(k)) with E*{[}log(W(k)){]} where the latter is
defined via bootstraping \citep{Tibshirani2001}.

On the other hand, we considered the following unweighted properties: a)
degree or the total number of trophic interactions, taking into account
in- and out-interactions (role as predator and prey, respectively); b)
trophic level or the position in the food web relative to primary
producers/detritus; and c) trophic similarity or the trophic overlap
between species based on shared and unique resources and consumers.

With the aim of studying the relationship between the interaction
strength of the species and its unweighted properties, we performed
linear regression analyses between the log(mean interaction strength)
and each of the mentioned unweighted properties. The statistical
significance of the fitted slopes was tested, as well as the difference
between the groups' slopes applying least-squares means
\citep{Harvey1960}.

Formulas used to obtain the above species properties are described in
Supplementary Material.

@@

Finally, we run extinction simulations and estimated its impact on the
stability of the network. For this, we calculated a stability index
called Quasi-Sign Stability (QSS), which is the proportion of stable
networks using randomized Jacobians and keeping the predator-prey sign
structure fixed \citep{Allesina2008}. With the aim of analysing the
effect of each species on the food web's stability, we deleted one
species at a time, so the network size was reduced by one. After each
species extinction, we calculated the QSS for the food web minus one
species (size = 489) and compared it with the QSS for the whole network
(size = 490); we performed 1000 simulations for each species. Then we
statistically analysed such difference with an Anderson-Darling test
\citep{Scholz1987}. The formula for the QSS is described in
Supplementary Material.

@@

In this work we have estimated the interaction strength for the most
highly-resolved marine food web to date, which comprises 490 species and
16041 predator-prey interactions (Figure 3). The distribution of the
interaction strength best fit to a log-Normal model, which indicates
that there is a prevalent skew towards weaker interactions (Figure 4,
Table 1).

Regarding the distribution of the species mean interaction strength, the
clustering method showed that species do form two distinct groups:
`High' and `Low' interaction strength (Appendix Fig. A1). The so-called
`High IS' and `Low IS' groups of species, exhibited different and for
some cases opposite relationships with unweighted properties. It's
noteworthy that only the relationship with trophic level revealed a
similar trend in the regression analysis for both groups: mean
interaction strength increases with trophic level (Figure 5A). On the
contrary, the linear regressions with degree and trophic similarity
showed opposite relationships between groups. This means that in species
with relatively higher interaction strength, `High IS', such strength
decreases when the number of interactions (degree) increases; the
opposite occurs in species with relatively lower interaction strength
`Low IS' (Figure 5B). Regarding trophic similarity, the interaction
strength decreases in `High IS' species while increases in `Low IS'
species (Figure 5C).

Linear regressions btw IS (weighted) and unweighted prop. Biplots btw
QSS difference and weighted and unweighted prop.

\clearpage
\conclusions[Conclusions]

@@

@@

\begin{figure}
\includegraphics[width=12cm]{Regressions} \caption{Relationships between weighted (interaction strength) and unweighted species properties. Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).}\label{fig:unnamed-chunk-5}
\end{figure}

\begin{table}[t]
\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web. According to AIC, log-Normal is the best model.}
\begin{tabular}{l c c c}
\tophline

@@

\appendixfigures
\clearpage

\begin{figure}
\includegraphics[width=12cm]{Clus_meanIS} \caption{A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web. B) Visualization of the optimal number of clusters applying the Gap statistic.}\label{fig:unnamed-chunk-6}
\end{figure}

@@
